ms2

### 2017-05-19 ms2/ms2.Rmd

```{r}
results %>%
  filter(model=='spearman') %>%
  mutate(bug_drug=interaction(bug, drug_group)) %>%
  ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  geom_linerange() +
  coord_flip()
```

@@

```{r hrr_spearman_models, cache=FALSE}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r univariate_models, cache=FALSE}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n) %>%
  kable
```

```{r}
results %>%
  filter(model=='univariate', term=='mean') %>%
  arrange(estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group),
         bug_drug=factor(bug_drug, levels=bug_drug, ordered=TRUE)) %>%
  ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  geom_linerange() +
  coord_flip()
```

@@

```{r}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  arrange(estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group),
         bug_drug=factor(bug_drug, levels=bug_drug, ordered=TRUE)) %>%
  ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  geom_linerange() +
  coord_flip()
```

@@

```{r cache=FALSE}
hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_multivariate_models, cache=FALSE}
sig_bug_drug = hrr_results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

@@

>>>>

```{r}
interval_plot = function(df) {
  arrange(df, estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group),
         bug_drug=factor(bug_drug, levels=bug_drug, ordered=TRUE)) %>% 
    ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
    geom_point() +
    geom_linerange() +
    coord_flip()
}

results %>%
  filter(model=='spearman') %>%
  interval_plot()
```

@@

```{r hrr_spearman_models}
hrr_results %>%
  filter(model=='spearman') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r univariate_models}
results %>%
  filter(model=='univariate', term == 'mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  #filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj, n) %>%
  kable
```

```{r}
results %>%
  filter(model=='univariate', term=='mean') %>%
  interval_plot()
```

@@

```{r}
results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  interval_plot()
```

@@

```{r}
hrr_results %>%
  filter(model=='multivariate', term==multivariate_term) %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.value < 0.05) %>%
  arrange(p.value) %>%
  select(bug, drug_group, estimate, p.value, p.adj) %>%
  kable
```

@@

```{r hrr_multivariate_models}
sig_bug_drug = hrr_results %>%
  filter(model=='univariate', term=='mean') %>%
  mutate(p.adj=p.adjust(p.value, method='BH')) %>%
  filter(p.adj < 0.05) %>%
  select(bug, drug_group)

@@

```{r}
left_join(state_abg, state_ineq, by=c('state', 'drug_group')) %>%
  filter(bug %in% c('E. coli', 'Eb. cloacae', 'CNST', 'MSSA', 'MRSA', 'S. pneumoniae')) %>%
  ggplot(aes(x=mean, y=mean_percent_nonsusceptible, color=drug_group, shape=bug)) +
  geom_point() +
  xlab('claims per beneficiary')
```
